---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# LTable (1.0.0)

This package is developed for those who wanna make quick LaTeX code for tables from the results obtained in R environment.

## How to install

You can install the package from my repo on GitHub by running
```{r install, eval=F}
devtools::install_github("yukai-yang/LTable")
```
provided that the package "devtools" has been installed beforehand.

## Example

After installing the package, you can attach the package by running
```{r attach}
library("LTable")
```

The "rules of the game" is that,

* you input matrices, data.frames, or lists of matrices and data.frames into "...",
* the elements in "..." will be binded by row,
* and if the element is a list, then its elements will be binded by column.

In the following, an example is offered, showing you how to write prompt LaTeX table code based on R objects: 

```{r example1}
x = matrix(rnorm(9),3,3)
y = data.frame(a=c('a','b','c','d'),b=1:4)
z = matrix(0,2,5)
```
The three R objects are: a matrix (x), a data.frame (y), and a matrix (z). Then we run the "LTable" function:
```{r example2}
LTable(y,caption="Hello!",list(round(x,2),z),label="tab:hi",indent=TRUE)
```
LaTeX code done!
